Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-13 paper/galsize_paper.tex
Corrected typos in figure captions

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=8cm]{FIGS/color_selected_size_dependent_clustering.pdf}
\caption{
{\bf Distinct $\rhalf-$dependence of clustering for color-selected galaxy samples.}
Projected clustering of SDSS galaxies in the bin of stellar mass: $10^{9.75}<\mstar/\msun<10^{10.25}.$ For both ``blue" and ``red" samples, we first divide SDSS galaxies falling in the $\mstar$ bin based on a color cut at $g-r=0.65.$ We then subsequently compute $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}}$. In analogy to the left panel of Figure \ref{fig:sizedefinition}, this sample definition results in identical stellar mass function for large and small subsamples, separately for both red and blue parent samples. We then measure $\wproj$ for each of the four subsamples, plotting the results with color-coding as specified in the legend. At this stellar mass, pre-selecting galaxy samples by color results in a dramatic weakening of the $\rhalf-$dependence of $\wproj$ relative to $\mstar-$complete samples, as well as a sign-reversal of the signal. In \S\ref{sec:interpretation} we give a simple halo model picture unifying the trends shown here with those illustrated in Figure \ref{fig:clustering_ratio_upshot}.
}
\label{fig:colorclustering}
\end{figure*}
%---------------------------------------------------------------------------------------------------

@@

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction.pdf}
\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm9p75_sm10p25.pdf}
\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction2.pdf}
\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm10p25_sm10p75.pdf}
\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction3.pdf}
\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm10p75_sm11p25.pdf}
\caption{
{\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, in the {\em left panels} we show predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}. To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which are reversed and weaker than the trends predicted here: for both blue and red samples, the observed $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies. As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be significantly stronger relative to large galaxies of the same stellar mass $\mstar\lesssim10^{11}\msun.$ We additionally predict that at sufficiently large mass $\mstar\gtrsim10^{11}\msun,$ the trend of small-scale $\Delta\Sigma$ with $\rhalf$ should reverse sign. The {\em right panels} display the physical explanation for this prediction. For $\mstar\lesssim10^{11}\msun,$ satellites preferentially populating the small sample heavily weight high-mass halos, boosting the lensing signal on all scales. For $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10\%,$ central galaxies dominate the signal, and the $\rvir-$based model predicts that $\rhalf$ increases with $\mhalo$ for centrals. See text for further details. 
}
\label{fig:lensingprediction}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

>>>>

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=8cm]{FIGS/color_selected_size_dependent_clustering.pdf}
\caption{
{\bf Distinct $\rhalf-$dependence of clustering for color-selected galaxy samples.}
Projected clustering of SDSS galaxies in the bin of stellar mass: $10^{9.75}<\mstar/\msun<10^{10.25}.$ For both ``blue" and ``red" samples, we first divide SDSS galaxies falling in the $\mstar$ bin based on a color cut at $g-r=0.65.$ We then subsequently compute $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}}$. In analogy to the bottom left panel of Figure \ref{fig:sizedefinition}, for each of the red and blue samples, the small and large subsamples have statistically indistinguishable stellar mass functions. We then measure $\wproj$ for each of the four subsamples, plotting the results with color-coding as specified in the legend. At this stellar mass, pre-selecting galaxy samples by color results in a dramatic weakening of the $\rhalf-$dependence of $\wproj$ relative to $\mstar-$complete samples, as well as a sign-reversal of the signal. In \S\ref{sec:interpretation} we give a simple halo model picture unifying the trends shown here with those illustrated in Figure \ref{fig:clustering_ratio_upshot}.
}
\label{fig:colorclustering}
\end{figure*}
%---------------------------------------------------------------------------------------------------

@@

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction.pdf}
\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm9p75_sm10p25.pdf}
\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction2.pdf}
\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm10p25_sm10p75.pdf}
\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction3.pdf}
\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm10p75_sm11p25.pdf}
\caption{
{\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, in the {\em left panels} we show predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}. To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the observed trends are reversed and weaker than those predicted here: for both blue and red samples, the observed $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies. As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show that $\Delta\Sigma$ of small galaxies is significantly stronger relative to large galaxies of the same stellar mass $\mstar\lesssim10^{11}\msun.$ We additionally predict that at sufficiently large mass $\mstar\gtrsim10^{11}\msun,$ the trend of small-scale $\Delta\Sigma$ with $\rhalf$ reverses sign. The {\em right panels} display the physical explanation for this prediction. For $\mstar\lesssim10^{11}\msun,$ satellites preferentially populating the small sample heavily weight high-mass halos, boosting the lensing signal on all scales. For $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10\%,$ central galaxies dominate the signal, and the $\rvir-$based model predicts that $\rhalf$ increases with $\mhalo$ for centrals. See text for further details. 
}
\label{fig:lensingprediction}
\end{figure*}
%-----------------------------------------------------------------------------------------------------
